### 2022-10-14 manuscript.Rmd
Fix model ouputs in supplement

```{r, ress1a}
# Helper function for printing model summary, ANOVA (F tests), and contrasts
print_model_outputs <- function(model_object) {
  model_object$summary$data <- NULL # Prevents cluttering the summary output
  print(model_object$summary$data)
  cat("\n")
  print(model_object$anova)
  cat("\nFollow-Up Contrasts (Simple Effects)\n")
  print(model_object$contrasts)
  cat("\n\n")
}

>>>>

```{r, ress1a}
# Helper function for printing model summary, ANOVA (F tests), and contrasts
print_model_outputs <- function(model_object) {
  model_object$summary$call$data <- NULL # Prevents cluttering the output
  print(model_object$summary)
  cat("\n")
  print(model_object$anova)
  cat("\nFollow-Up Contrasts (Simple Effects)\n")
  print(model_object$contrasts)
  cat("\n\n")
}
